\resumeSubHeadingListStart

  \resumeSubheading
    {Amazon}{Jun. 2026 \textemdash\ Aug. 2026}
    {Incoming Software Development Engineer Intern $|$ FinTech Org}{Arlington, VA}

  \resumeSubheading
    {\href{https://physics.gatech.edu/}{Georgia Tech School of Physics}}{Jan. 2026 \textemdash\ Present}
    {Web Developer}{Atlanta, GA}
    \resumeItemListStart
      \resumeItem{Ensured continuous Drupal uptime \& optimized UX with responsive \textbf{HTML/CSS} for \textbf{59K+ monthly visitors}.}
    \resumeItemListEnd

  \resumeSubheading
    {Georgia Tech Bhamla Lab}{Aug. 2024 \textemdash\ Dec. 2025}
    {Computational Researcher}{Atlanta, GA}
    \resumeItemListStart
      \resumeItem{Engineered \textbf{MATLAB stochastic simulations} \& constructed Bluetooth \textbf{Arduino} robots to model \& validate control frameworks for pairwise \& ternary herding behaviors.}
      \resumeItem{Designed financial simulations with \textbf{LangGraph LLM agents} \& \textbf{Pandas} to apply herding dynamics to market traders.}
    \resumeItemListEnd
    \vspace{-8pt}

  \resumeSubheading
    {Georgia Tech School of Civil Engineering}{Jan. 2024 \textemdash\ May 2024}
    {Computer Vision Researcher}{Atlanta, GA}
    \resumeItemListStart
      \resumeItem{Engineered a custom \textbf{High Boost filter mask} \& tuned parameters to optimize baseline street crack registration models, driving a \textbf{140\% increase} in registration quality.}
      \resumeItem{Architected custom \textbf{image interpolation techniques} to salvage failed registrations from a 6-year 3D laser dataset, yielding a \textbf{500\% increase in recall} \& a \textbf{263\% increase in precision}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd